%-------------------------
% Resume in Latex
% Author : Kishan Seksaria
%------------------------

\documentclass[letterpaper,11pt]{article}

% Conditional logic to generate two versions of the resume with different phone numbers
\newif\ifaltphone

% Check if \altphone is defined by the Makefile
\ifdefined\altphone
  \ifnum\pdfstrcmp{\altphone}{true}=0
    \altphonetrue
  \else
    \altphonefalse
  \fi
\else
  \altphonefalse % Default fallback
\fi

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{lmodern}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\footskip}{4.08003pt}
\input{glyphtounicode}


%----------FONT OPTIONS---------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small#2} \\
      \textit{\small#3} & \textit{\small#4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[1]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
  {\Huge \textsc{Kishan Seksaria}} \\ \vspace{5pt}  % 1359 1/2 W Adams Blvd, Los Angeles, CA 90007 \\ \vspace{1pt}
  \small{\ifaltphone
    \faIcon{mobile-alt} +91 98836 34750 % Your alternative phone
  \else
    \faIcon{mobile-alt} +1 (213) 284-5282 % Your original phone
  \fi ~ \href{mailto:kishanseksaria@gmail.com}{\raisebox{-0.1\height}\faEnvelope\ {kishanseksaria@gmail.com}} ~ \href{https://www.linkedin.com/in/kishan-seksaria/}{\raisebox{-0.1\height}\faLinkedin\ {Kishan Seksaria}} ~ \href{https://github.com/KishanSeksaria}{\faGithub\ {KishanSeksaria}}}
  \vspace{-8pt}
\end{center}

%---------SUMMARY-----------
\section{Summary}
\small{Master's student in Computer Science at USC (May 2025). Experienced in full-stack development with React, Angular, Node.js, Spring Boot, and SwiftUI. Currently working on RAG and LLM projects. Seeking Software Developer role to leverage technical skills in building innovative applications.}
\vspace{-8pt}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Southern California}{Aug, 2023 -- May 2025 (expected)}
{Master of Science in Computer Science}{Los Angeles, CA}
\vspace{-2pt}
{\item{Coursework: Analysis of Algorithms, Database Systems, Web Technologies, Artificial Intelligence, Machine Learning, Security Systems, Information Retrieval}}
\vspace{-5pt}
\item{GPA: 3.78/4.0}
\vspace{2pt}

\resumeSubheading
{Maulana Abul Kalam Azad University Of Technology}{Aug, 2019 -- Jul, 2023}
{Bachelor of Technology in Computer Science and Engineering}{Kolkata, India}
\vspace{-2pt}
\item{\textbf{GPA:} 9.31/10.0}

\resumeSubHeadingListEnd
\vspace{-16pt}

%------RELEVANT COURSEWORK-------
% \section{Relevant Coursework}
% %\resumeSubHeadingListStart
% \begin{multicols}{4}
%   \begin{itemize}[itemsep=-5pt, parsep=5pt]
%     \item Data Structures
%     \item Analysis of Algorithms
%     \item Database Systems
%     \item Web Technologies
%     \item Artificial Intelligence
%     \item Machine Learning
%     \item Security Systems
%     \item Computer Networks
%   \end{itemize}
% \end{multicols}
% \vspace*{2.0\multicolsep}
%\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{\textbf{Languages:}{ Java, Javascript, Python, Typescript, Swift, C, C++, HTML, CSS}}}
  \vspace{-4pt}
  \small{\item{\textbf{Frameworks:}{ Node.js, Express, Next.js, Angular, React, SwiftUI, Spring Boot}}}
  \vspace{-4pt}
  \small{\item{\textbf{Databases:}{ MongoDB (Hands-on), SQL (Theoretical), Vector Databases (Learning)}}}
  \vspace{-4pt}
  \small{\item{\textbf{Cloud \& Deployment:}{ Google Cloud Platform (GCP), Azure, AWS, Docker }}}
  \vspace{-4pt}
  \small{\item{\textbf{AI/ML Technologies:}{ Retrieval-Augmented Generation (RAG), Large Language Models (LLM), LangChain}}}
  \vspace{-4pt}
  \small{\item{\textbf{Tools:}{ Git, Github, Github Actions, VS Code, Postman, Maven, Microsoft Office, LaTeX, HighCharts}}}
  \vspace{-4pt}
\end{itemize}
\vspace{-12pt}


%-----------PROJECTS-----------
\section{Projects}
\vspace{-2pt}
\resumeSubHeadingListStart

% Go Shell
\resumeProjectHeading
{\textbf{Custom Shell Implementation \href{https://github.com/KishanSeksaria/codecrafters-shell-go}{\faGithub}} \\
  \emph{Go, Unix System Programming, Shell Scripting} & {Dec, 2024}}
\vspace{-3pt}
\resumeItemListStart
\resumeItem{Developed a Linux shell in Go, implementing built-in commands like echo, cd, pwd, exit, cat, and type.}
\resumeItem{Enabled execution of external commands from the system’s PATH, integrating a REPL for user interaction.}
\resumeItem{Strengthened error handling to manage invalid commands, enhancing shell stability and usability.}
\resumeItemListEnd
\vspace{-7pt}

%  iOS App
\resumeProjectHeading
{\textbf{Stock Summary iOS Application \href{https://drive.google.com/file/d/13OWHwxpiQEl2slM0-ieL7HKOwFjjfK7o/view?usp=sharing}{\faLink}} \\
  \emph{Swift, SwiftUI, Finnhub, HighCharts} & {Apr, 2024 -- May, 2024}}
\vspace{-3pt}
\resumeItemListStart
\resumeItem{Developed an iOS stock tracking app using Swift and SwiftUI, integrating Finnhub API for real-time stock data.}
\resumeItem{Implemented data visualization with Highcharts, creating interactive graphs for easy stock data analysis.}
\resumeItem{Enhanced user engagement with favorite stocks tracking and simulated trading, allowing users to track prices and simulate buying/selling with a wallet balance.}
\resumeItemListEnd
\vspace{-7pt}

%  Angular Website
\resumeProjectHeading
{\textbf{Stock Summary Single Page Web Application \href{https://stock-search-xvhu.onrender.com}{\faLink}} \\
  \emph{Typescript, Angular, Nodejs, Express, MongoDB, Finnhub, HighCharts} & {Feb, 2024 -- Apr, 2024}}
\vspace{-3pt}
\resumeItemListStart
\resumeItem{Built an Angular SPA with Finnhub API for real-time stock data, using RxJS and route caching to reduce API calls by 50\%.}
\resumeItem{Created a RESTful backend with Node.js, and MongoDB, integrating HighCharts for interactive data visualization.}
\resumeItem{Implemented CI/CD with GitHub Actions for automated Azure deployment, improving development workflow efficiency.}
\resumeItemListEnd
\vspace{-15pt}

% AI Game Agent
% \resumeProjectHeading
% {\textbf{AI Othello/Reversi Gameplay Agent \href{https://github.com/KishanSeksaria/CSCI-561---Foundations-of-AI/tree/main/hw2}{\faGithub}} \\
%   \emph{Python, Minimax Algorithm}}
% \vspace{-3pt}
% \resumeItemListStart
% \resumeItem{Implemented a game-playing agent using the Minimax algorithm, winning 100\% of games it has been tested on.}
% \resumeItem{Developed a heuristic evaluation function to assess game states and determine optimal moves.}
% \resumeItem{Optimised the algorithm using alpha-beta pruning to return the best move within 1s on average.}
% \resumeItemListEnd
% \vspace{-6pt}

%  REST API
% \resumeProjectHeading
% {\textbf{Social Media REST API \href{https://github.com/KishanSeksaria/social-media-REST-api}{\faGithub}} \\
%   \emph{Javascript, Node.js, Express, MongoDB, Passport.js} & {Jan, 2022}}
% \vspace{-3pt}
% \resumeItemListStart
% \resumeItem{Developed a versatile API for user interactions, leveraging Passport.js for secure authentication and access control.}
% \resumeItem{Utilized Mongoose for MongoDB connectivity, optimizing schema design for efficient data management.}
% \resumeItem{Established CRUD endpoints for seamless user interactions with social media content.}
% \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-6pt}

%-----------Professional Development & Leadership Experience-----------
\section{Professional Development \& Leadership Experience}
\resumeSubHeadingListStart
\resumeSubheading
% {GRIDS USC \href{https://drive.google.com/file/d/1mZmnyppT8QEj3XK9_qyv-jC2dngnn03G/view?usp=sharing}{\faLink}}{Apr, 2022 -- Jun, 2022}
{GRIDS USC}{Feb, 2025 -- Present}
{E-Board Member - Web Team}{Los Angeles, CA}
\vspace{-2pt}
\resumeItemListStart
\resumeItem{Leading the development of Trojan Square, a platform aimed at becoming a central hub for USC students.}
\resumeItem{Currently spearheading the creation of Ask USC AI, utilizing RAG (Retrieval-Augmented Generation) and LLMs (Large Language Models) to provide instant and accurate answers to student queries.}
\resumeItem{Planning future expansions like a student marketplace and other innovative features to make the platform future-proof.}
\resumeItemListEnd
\vspace{5pt}

\resumeSubheading
{Cognizant \href{https://drive.google.com/file/d/1mZmnyppT8QEj3XK9_qyv-jC2dngnn03G/view?usp=sharing}{\faLink}}{Apr, 2022 -- Jun, 2022}
{Fullstack Developer Trainee}{Kolkata, India}
\vspace{-2pt}
\resumeItemListStart
\resumeItem{Completed structured training on React.js and Java Spring Boot, enhancing understanding of full-stack development.}
\resumeItem{Gained hands-on experience through coding exercises and practical assignments.}
\resumeItem{Explored concepts of cloud computing, testing frameworks (JUnit, Mockito), and DevOps tools.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-12pt}

%-----------INVOLVEMENT---------------
\section{Achievements}
\resumeItemListStart
\resumeItem{Secured 1st position for two consecutive years in a coding competition at the state level, competing against 40+ colleges and 450+ participants.}
\resumeItemListEnd

\end{document}
